%if you are looking to edit LaTex files in VSC I highly reccomend checking out this tutorial https://github.com/James-Yu/LaTeX-Workshop/wiki/Install

\documentclass{article}
\usepackage[utf8]{inputenc}

\title{Pybullet Documentation}
\author{Jack Rivera}
\date{August 2020}

\begin{document}

\section{Pybullet Documentation Extended}

\vspace{0.4cm}
\textbf{softBodyAnchor} (int body1, int link1, int body2, int link2, vec3 offset)
\newline Pins vertex of a soft body to the vertex of a rigid/multi body or world. Returns constraint unique ID. See removeConstraint API to remove constraint
\vspace{0.2cm}
\newline @param
\begin{itemize}
    \item body1 - a non-negative integer denoting the body unique id of a deformable
    \item link1 - an integer denoting the index of the link. Default is -1 for the base
    \item body2 - a non-negative integer denoting the body unique id of a rigid/multibody with vertices defined (e.g. obj). Default is -1 for the world
    \item link2 - an integer denoting the index of the link. Default is -1 for the base
    \item offset (optional) - unclear
\end{itemize}
@return - an integer denoting the constraint unique ID
\vspace{0.4cm}
\newline
\textbf{getMeshData} (int bodyID)
\newline Experimental API used to mesh information (indices, vertices)
\vspace{0.2cm}
\newline @param
\begin{itemize}
    \item bodyID - a non-negative integer denoting the body unique id of a mesh
    \item note: other params outlined in pybullet doc do not appear to work
\end{itemize}
@return - a tuple (numVertices, (vertices)) where each vertex in 'vertices' is a tuple (x,y,z) and their index in 'vertices' is their corresponding link index

\section{General Simulation Notes}
\begin{itemize}
    \item Parameters: lame parameters (mu, lambda), damping (of single deformable), mass of block, center of mass, offset from parent position, collision margin (currently const). 
    \item For the simulation not to crash, a hole is needed in the new deformable architecture (inner rigid inside of a deformable cover)
          This is most likely due to a watertight requirement by the simulation. The current hole size we have been using has 0.1 m radius because
          anything too small (e.g 0.01 m) causes the mesh geometry to greatly increase in complexity around the hole causing the simulation to crash.
    \item numerical stability/stability of simulation is dependent on lame parameters and collision margin
    \item speed of simulation is dependent on density of mesh (empirically proven to be dominant factor in comparison to
          disabling collisions between internal rigid and outer deformable)
    \item To enable collisions between deformables, a collision margin must be set. WARNING: collision margin is very volatile. If the collision marign is set too high in comparison to width of deformable,
          the deforamble can collapse upon itself until it disappears or cause unphysical interactions (ejecting colliding objects)
    \item Currently, a resolution of 2 (gmsh element size factor), 60\% of outer dimensions for inner rigid body, and a 0.01
          has proven to be a stable and fast set of parameters for deformable cubes
\end{itemize}

\section{URDF Deformable Support}
\begin{itemize}
    \item The 'neohookean' tag of a 'deformable' takes it's 'mu' and 'lambda' parameters (the lame parameters) in kPa (This is suspected given 60 mu and 200 lambda work and 60 Kpa =0.06 MPa which is close to the approximated 0.1 MPa for hyperelastic material elastin).
    \item The 'virtual' tag of a 'deformable' is constrained to only a 'filename' attribute that loads a vtk/obj file. The deformable can only be relocated upon loading (loadURDF) and therefore cannot have a changed center of mass given you cannot specify an inertial reference frame relative to a nonexistent link reference frame
    \item loadSoftBody can support a spring model and neohookean model while URDF only supports neohookean (URDF also allows setting inertial properties)
    \item The only known supported URDF element tags for deformables: 'collision\_margin', 'repulsion\_stiffness', 'friction', 'neohookean'.
\end{itemize}

\section{Lame Parameter Notes}
\begin{itemize}
    \item The General Rule: $\mu \leq \lambda$
    \item The difference between $\mu$ and $\lambda$ cannot be too large (e.g. $<$ 400) but to be honest you should use your reference of phsyical properties to guide yourself. For example,
    elastic moduli ($\mu$) should be at least be 60 MPa because anything lower becomes too hyperelastic for the simulation to handle.
    \item My general rule is to start out at a decent Young's Modulus, increase $\lambda$ from the $\mu$ value until the simulation breaks and then everything
    is fair game. In other words, from the value of a decent Young's Modulus until the breaking lambda, any combination of two values in that range as long as the general rule is true should not break the simulation
    \item too many hyperelastic pieces will cause the sim to crash so as the number of nehookean pieces grow, the stiffer each one should become
    \item Generally, one could make the deformable stiffer by increasing the value of the Young's Modulus
          and in effect increasing lambda or by decreasing the difference between the two values.
\end{itemize}
\end{document}
